NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-06-01 ms_nihao_budget.tex
Add some content on HI and OVI absorption line and cite Thales' paper in Introduction

\def \etal {et~al.~}
\def \eg{e.g.}
\def \Section{\S}
\def \spose#1{\hbox  to 0pt{#1\hss}}  
\def \lta{\mathrel{\spose{\lower 3pt\hbox{$\sim$}}\raise  2.0pt\hbox{$<$}}}
\def \gta{\mathrel{\spose{\lower  3pt\hbox{$\sim$}}\raise 2.0pt\hbox{$>$}}}
\def \ion#1#2{#1{\footnotesize{#2}}\relax}
\def \ha       {H$\alpha$}
\def \hi       {\ion{H}{I}}
\def \hii      {\ion{H}{II}}
\def \oii      {[\ion{O}{II}]}

@@

{\bf The circum galactic medium (CGM) is a major potential  reservoir
  of the missing baryons.}  Recent advances in the detection of  gas
in the CGM have come  from the COS survey \citep{Tumlinson11,
  Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
mass haloes $\Mhalo \sim 10^{12}\Msun$ a significant amount of warm
($10^4 < T < 10^7$K) gas has been detected \citep{Werk14}, accounting
for 33-88\% of the baryon budget. In the future such observations will
be extended to a wider range of halo masses.
%{\bf ??? To understand
%  the physical properties of the CGM and the origins of components in
%  each phase has been shown to be able to test the impact of feedback
%  models \citep{Sharma12,Marasco13}???
  {\bf The physical properties of the CGM has been shown to be able to
    test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
    predicted galactic halo baryon fractions of galaxies with halo
    masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
    cosmological hydrodynamical simulations with a well-constrained
    model for galactic outflows.  They found that, without the outflow
    model, the baryon fraction inside the virial radius is roughly the
    cosmic baryonic fraction, but with the outflow model, the baryon
    fraction is increasingly suppressed in lower mass haloes.  By
    comparing results at $z=3$ and $z=0$, they showed that large
    haloes remove their baryons at early times while small haloes lose
    baryons more recently due to the wind material taking longer to
    return to low-mass galaxies than high-mass galaxies.
%  
  \citet{Sokolowska16} studied the halo gas of three Milky way-sized
  galaxies using cosmological zoom-in simulations. They found that
  most of missing baryons actually resides in warm-hot and hot gas
  which contribute to 80\% of the total gas reservoir.  The recovered
  baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
  is sensitive to the feedback model so that a reliable spatial
  mapping of the warm-hot medium will provide  a stringent test for
  feedback models.}

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project. NIHAO galaxies are consistent with the stellar mass vs halo
mass relations from halo abundance matching since redshift $z\sim 4$
\citep{Wang15}, the galaxy star formation rate vs stellar mass
relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore,
the simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.  {\bf Mention Gutcke et al. 2016}

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\def \etal {et~al.~}
\def \eg{e.g.}
\def \Section{\S}
\def \spose#1{\hbox  to 0pt{#1\hss}}  
\def \lta{\mathrel{\spose{\lower 3pt\hbox{$\sim$}}\raise  2.0pt\hbox{$<$}}}
\def \gta{\mathrel{\spose{\lower  3pt\hbox{$\sim$}}\raise 2.0pt\hbox{$>$}}}
\def \ion#1#2{#1{\footnotesize{#2}}\relax}
\def \ha       {H$\alpha$}
\def \hi       {\ion{H}{I}}
\def \hii      {\ion{H}{II}}
\def \oii      {[\ion{O}{II}]}
\def \ovi      {\ion{O}{VI}}

@@

{\bf The circum galactic medium (CGM) is a major potential  reservoir
  of the missing baryons. \hi{} and metal absorption lines are expected 
to exhibit such diffuse baryonic content. \hi{} is mainly from gas with
temperature T $\sim 10^4$ K so that it is able to detect cold gas in CGM.
Meanwhile, theoretical work has predicted that a substaince portion of 
CGM is in warm or hot phase with temperature T $> 10^{4.5}$ K, either
through photoionization, accretion shock or shock caused by galactic winds
\citep{voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, the detection
is dominated by metal line, e.g. \ovi{}.}  Recent advances in the detection of gas
in the CGM have come  from the COS survey \citep{Tumlinson11,
  Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
mass haloes $\Mhalo \sim 10^{12}\Msun$ a significant amount of warm
($10^4 < T < 10^7$K) gas has been detected \citep{Werk14}, accounting
for 33-88\% of the baryon budget. In the future such observations will
be extended to a wider range of halo masses.
{\bf A number of large volume cosmological simulations \citep{Ford13, Ford15,
Suresh15b, Oppenheimer16} and zoom-in cosmological simulations \citep{Stinson12,
Hummels13, Shull14} have given the prediction for the \hi{} and
\ovi{} absorption line. \citet{Gutcke16}
compared the column density profile of \ovi{} and \hi{} in CGM of galaxies
of the cosmological hydrodynamical simulation suite NIHAO \citep{Wang15}
with observations, studied the covering fraction of dense \hi{}, looked
at the shape of the CGM and its chemical composition. The conclusion
shows the simulations can reproduce the observation properties well.}

%{\bf ??? To understand
%  the physical properties of the CGM and the origins of components in
%  each phase has been shown to be able to test the impact of feedback
%  models \citep{Sharma12,Marasco13}???
  {\bf The physical properties of the CGM has been shown to be able to
    test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
    predicted galactic halo baryon fractions of galaxies with halo
    masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
    cosmological hydrodynamical simulations with a well-constrained
    model for galactic outflows.  They found that, without the outflow
    model, the baryon fraction inside the virial radius is roughly the
    cosmic baryonic fraction, but with the outflow model, the baryon
    fraction is increasingly suppressed in lower mass haloes.  By
    comparing results at $z=3$ and $z=0$, they showed that large
    haloes remove their baryons at early times while small haloes lose
    baryons more recently due to the wind material taking longer to
    return to low-mass galaxies than high-mass galaxies.
%  
  \citet{Sokolowska16} studied the halo gas of three Milky way-sized
  galaxies using cosmological zoom-in simulations. They found that
  most of missing baryons actually resides in warm-hot and hot gas
  which contribute to 80\% of the total gas reservoir.  The recovered
  baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
  is sensitive to the feedback model so that a reliable spatial
  mapping of the warm-hot medium will provide  a stringent test for
  feedback models.}

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project. NIHAO galaxies are consistent with the stellar mass vs halo
mass relations from halo abundance matching since redshift $z\sim 4$
\citep{Wang15}, the galaxy star formation rate vs stellar mass
relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore,
the simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.

@@

%
\bibitem[Ford et al.(2013)]{Ford13} Ford, A.~B., Oppenheimer, B.~D., Dav{\`e}, R., et al.\ 2013, \mnras, 432, 89

%
\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2015, arXiv:1503.02084

@@

% NIHAO VIII:
\bibitem[Gutcke et al.(2016)]{Gutcke16} Gutcke, T.~A., Stinson, G.~S., Macci{\`o}, A.~V., et al.\ 2016, arXiv:1602.06956

@@

%
\bibitem[Hummels et al.(2013)]{Hummels13} Hummels, C.~B., Bryan, G.~L., Smith, B.~D., et al.\ 2013, \mnras, 430, 1548

@@

%
\bibitem[Oppenheimer et al.(2016)]{Oppenheimer16} Oppenheimer, B.~D., Crain, R.~A., Schaye, J., et al.\ 2016, arXiv:1603.05984

@@

%
\bibitem[Shull (2014)]{Shull14} Shull, J.~M.\ 2014, \apj, 784, 142

@@

%
\bibitem[Stinson et al.(2012)]{Stinson12} Stinson, G.~S., Brook, C., Prochaska, J.~X., et al.\ 2012, \mnras, 425, 129

@@

%
\bibitem[Suresh et al.(2015)]{Suresh15b} Suresh, J., Rubin, K.~H.~R., Kannan, R., et al.\ 2015, arXiv:1511.00687

@@

% Properties of gas in and around galaxy haloes
\bibitem[van de Voort \& Schaye (2012)]{voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991
